### 2024-11-15 conteudo/eval/eval.tex
fix missing end of paragraph

The results in Table \ref{tab:emp} show that as the similarity metric decreases, there is a notable increase in function pairs that are not duplications within the Linux kernel. For similarity ranges of 79\%-81\% or higher, there is a high percentage of code duplications. At 69\%-71\% similarity, the duplication rate drops to 50%. At 59\%-61%, it further decreases to 20%, and below 49\%-51%, no code duplications were found.

>>>>

The results in Table \ref{tab:emp} show that as the similarity metric decreases, 
there is a notable increase in function pairs that are not duplications within 
the Linux kernel. For similarity ranges of 79\%-81\% or higher, there is a high 
percentage of code duplications. At 69\%-71\% similarity, the duplication rate 
drops to 50\%. At 59\%-61\%, it further decreases to 20\%, and below 49\%-51\%, 
no code duplications were found.
